\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{setspace}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Set up section title formats
\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{0.5em}\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

% Adjust paragraph spacing
\setlength{\parskip}{0.5em}
\setstretch{1.15}

\begin{document}

% Header with icons
\begin{center}
    {\huge \textbf{Yihui Gong}} \\
    \vspace{0.5em}
    \faPhone\ Phone: 07529963251 \quad
    \faEnvelope\ Email: gyh1429107530@gmail.com
\end{center}

% Professional Summary
\section*{\faUser\ Professional Summary}
A highly skilled computer science graduate student specializing in data statistics, machine learning, and mathematical analysis. Experienced in developing both web-based and native Java applications, fluent in Chinese and English, enabling seamless cross-cultural collaboration. With a solid foundation in data structures, data mining, and machine learning (decision trees, clustering, logistic regression, Bayesian methods), I excel in data modeling and efficient analysis. Proficient in Python, Vue.js, and FastAPI for web application development, and known for excellent teamwork and project management skills.

% Work Experience
\section*{\faBriefcase\ Work Experience}

\textbf{Software Engineer} \hfill November 2022 – January 2023 \\
Personal Project – Southampton, United Kingdom
\begin{itemize}[noitemsep,topsep=0pt]
    \item Designed and developed the front-end interface using Vue.js, enhancing user interaction.
    \item Implemented secure communication protocols with Python and FastAPI, ensuring information security.
    \item Integrated cryptographic libraries for secure messaging, reducing response time by 50\%.
    \item Increased user satisfaction by 80\% through improved security features and performance optimization.
\end{itemize}

\textbf{HackAI2023 Competition} \hfill February 2023 \\
Southampton, United Kingdom
\begin{itemize}[noitemsep,topsep=0pt]
    \item Participated in the HackAI competition to predict future aviation load factors using extensive data.
    \item Responsible for data cleaning, handling regional GDP, airlines, routes, and COVID-19 data.
    \item Achieved 83\% accuracy with Random Forest, contributing to a third-place finish.
\end{itemize}

\textbf{Multiple Image Semantic Style Transfer and Evaluation System} \hfill October 2022 – April 2023 \\
University of Southampton – Southampton, United Kingdom
\begin{itemize}[noitemsep,topsep=0pt]
    \item Focused on semantic preservation and stylization quality across multiple images.
    \item Established a quantitative evaluation system based on content preservation and style transfer effectiveness.
    \item Developed an encoder-decoder architecture with residual blocks, using VGG network for feature extraction.
    \item Employed SequenceNet and U-Net as loss networks to achieve semantic preservation.
    \item Conducted user surveys to validate the effectiveness of the evaluation system.
\end{itemize}

\textbf{Automatic Authenticity Detection of Tweets} \hfill September 2022 – February 2023 \\
Southampton, United Kingdom
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed an automatic authenticity detection system for tweets using NLP and machine learning algorithms.
    \item Responsible for preprocessing and feature extraction.
    \item Utilized Skip-gram for Word2Vec transformation, inputting into a Transformer model for classification.
\end{itemize}

\textbf{Programming Language Development} \hfill March 2022 – June 2022 \\
Southampton, United Kingdom
\begin{itemize}[noitemsep,topsep=0pt]
    \item Designed and implemented a programming language using Haskell for processing Excel files.
    \item Used 'happy' as a compiler generator to build a custom language compiler.
    \item Developed syntax and semantic rules to meet data processing requirements.
    \item Optimized language performance to improve efficiency in Excel data processing.
    \item Implemented operations like data reading, cleaning, and analysis on Excel files.
\end{itemize}

\textbf{Distributed File Storage System Developer} \hfill February 2021 – April 2021 \\
Southampton, United Kingdom
\begin{itemize}[noitemsep,topsep=0pt]
    \item Designed and implemented a system supporting concurrent client operations.
    \item Developed a rebalancing algorithm to ensure data availability during node failures.
    \item Established persistent TCP connections for continuous communication between components.
    \item Created a file indexing system to effectively track stored files and manage file lifecycles.
\end{itemize}

% Skills with icons
\section*{\faTools\ Skills}
\begin{itemize}[noitemsep,topsep=0pt]
    \item \textbf{Programming Languages}: Java, Python, C++, Haskell, JavaScript
    \item \textbf{Web Development}: Vue.js, FastAPI, HTML, CSS
    \item \textbf{Data Science}: Machine Learning, Deep Learning, Reinforcement Learning, NLP, Computer Vision
    \item \textbf{Tools and Technologies}: Apache Kafka, ZooKeeper, TensorFlow, PyTorch
    \item \textbf{Security}: Encryption protocols, Data encryption, Secure communication implementation
    \item \textbf{Office Software}: Microsoft Office (Word, Excel, PowerPoint)
\end{itemize}

% Education with icon
\section*{\faGraduationCap\ Education}
\textbf{Master of Computer Science} \hfill February 2024 – Expected December 2025 \\
University of Sydney – Sydney, Australia

\textbf{Bachelor of Computer Science} \hfill June 2023 \\
University of Southampton – Southampton, United Kingdom

% Languages with icon
\section*{\faLanguage\ Languages}
\begin{itemize}[noitemsep,topsep=0pt]
    \item English (IELTS 6.5), Chinese (Native)
\end{itemize}

% Interests with icon
\section*{\faFutbol\ Interests}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Badminton, Swimming
\end{itemize}

\end{document}
